Viscous Erosion in Porous Media

### 2018-02-26 docs/TexNotes/Notes.tex
NM

\subsection{The vanishing rate of the area}
The rate of area loss is given by
\begin{equation}
\dot{A} = - \abs{\tau} L
\end{equation}
We then insert the scaling $\abs{\tau} \sim -1/(L \log L)$ and simplify to get
\begin{equation}
\dot{A} = C/\log{A}
\end{equation}
which we solve to get
\begin{equation}
A (1 - \log A) = C (t_f - t)
\end{equation}
In particular, I believe the signs are correct here.
BUT, I am not so sure of this calculation anymore, now that $W$ is included.

>>>>

\subsection{The vanishing rate of the area}

The area loss rate is given by
\begin{align}
\dot{A} = - \int_{\gamma} \atau \, ds \,  = - \mean{\atau} L \, .
\end{align}
The above is an exact relation. Substitution of the scaling law gives
\begin{align}
\dot{A} \sim \frac{ - \mu V}{\log(W/L)} \, .
\end{align}
Inserting $A \sim L^2$ and rearranging gives
\begin{align}
\log (C_2 A/W^2) dA = C_1 \mu V dt
\end{align}
Integrating gives
\begin{align}
A \left(1 - \log(C_2 A/W^2) \right) = C_1 \mu U (t_f - t)
\end{align}
In the limit of $A \to 0$, the log-term on the left-hand-side will win, giving
\begin{align}
A(1 - \log(A) ) \sim c_A (t_f - t)
\end{align}
I have kept the one above, just so the graph of the scaling law doesn't look funny for bigger $A$.

\vsp{5}
TO KILL:

The rate of area loss is given by
\begin{equation}
\dot{A} = - \abs{\tau} L
\end{equation}
We then insert the scaling $\abs{\tau} \sim -1/(L \log L)$ and simplify to get
\begin{equation}
\dot{A} = C/\log{A}
\end{equation}
which we solve to get
\begin{equation}
A (1 - \log A) = C (t_f - t)
\end{equation}
In particular, I believe the signs are correct here.
BUT, I am not so sure of this calculation anymore, now that $W$ is included.

### 2018-02-26 docs/methods/erosion_methods.tex
NM

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[htbp]
\begin{center}
\includegraphics[width = 0.8 \textwidth]{./figs/area_drag.pdf}
\caption{One body}
\label{}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% Figure from datafile 01circ1024aa;
% Uses 01circ1024.in with epsfac = 10, sigfac = 10, dt = 1e-6, fixarea = 0, fixpdrop = 0

The body's rate of area reduction is given by integrating the absolute shear stress around the boundary
\begin{align*}
  \dot{A} = - \int_{\gamma} \atau \, ds \,  = - \mean{\atau} L \, .
\end{align*}
Thus, the area-loss rate is given by the product of the mean shear
$\mean{\atau}$ and the total perimeter $L$. Inserting scaling law~\eqref{eqn:stresslaw} gives
\begin{align*}
  \dot{A} \sim \frac{\mu \umax}{\log(W/L)} \, .
\end{align*}
Noting that $A \sim L^2$ allows one to solve the ODE to determine how the body area changes with time
\begin{align*}
  A (1 - \log A) = \areaconst (t_f - t)
\end{align*}
where $c_A$ is a constant.
This is an {\em implicit} relationship for how the area scales down in time during erosion. In Fig.~6a, we show the body area as a function of time measured in the simulation against the above scaling law with $\areaconst = 0.42$.

\todo[inline]{Explain the drag here too}

>>>>

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[htbp]
\begin{center}
\includegraphics[width = 0.9 \textwidth]{./figs/area_drag.pdf}
\caption{The area and drag of an eroding body: (a) The body area measured in the simulations (black) shown against the scaling-law prediction \eqref{area_predict} (dotted red). The two are nearly indistinguishable. (b) The horizontal drag (black) on the body as it erodes, along with the viscous (green) and pressure (blue) contributions. The scaling prediction can be rearranged to give estimate \eqref{viscdrag} for the viscous drag (dotted red).}
\label{area_drag}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% Figure from datafile 01circ1024aa;
% Uses 01circ1024.in with epsfac = 10, sigfac = 10, dt = 1e-6, fixarea = 0, fixpdrop = 0

The body's rate of area reduction is given by integrating the absolute shear stress around the boundary
\begin{align}
\dot{A} = - \int_{\gamma} \atau \, ds \,  = - \mean{\atau} L \, .
\end{align}
Thus, the area-loss rate is given by the product of the mean shear
$\mean{\atau}$ and the total perimeter $L$. Inserting scaling law~\eqref{eqn:stresslaw} gives
\begin{align}
\dot{A} \sim \frac{ - \mu \umax}{\log(W/L)} \quad \text{as } L \to 0 \, . 
\end{align}
Noting that $A \sim L^2$ allows one to solve the ODE to determine how the body area changes with time
\begin{align}
\label{area_predict}
A (c_1 - \log A) \sim c_2 (t_f - t) \qquad \text{as } t \to t_f \, .
\end{align}
where $c_1$ and $c_2$ are constants.
This is an {\em implicit} relationship for how the area scales down in time during erosion. In Fig.~\ref{area_drag}a, we show the body area as a function of time measured in the simulation against the above scaling law with $c_1 =2.2$ and $c_2 = 30$. The comparison shows close agreement between the two (they are indistinguishable).

In Fig.~\ref{area_drag}(b), we show the drag $F_D$ measured on the body as it erodes. The drag decreases gradually, then takes a nose dive in the final moments when the body vanishes, as is consistent with the logarithmic dependence on lengthscale $L$ in 2D Stokes flow. We also show in the figure the separate contributions of the viscous and the pressure drag. As a final check, are scaling estimates for area change can be rearranged to estimate the viscous drag component
\begin{align}
\label{viscdrag}
F_{\mu} \approx \mean{\atau} L \sim \frac{c_2}{-\log A + c_1 -1}
\end{align}
This scaling law is shown in the figure (red, dotted curve) and shows good agreement with the viscous drag. Of course, \eqref{viscdrag} is less accurate than the previous estimates since it does not take into account the normal direction of the surface, only the mean shear stress.
